Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing changes to paper.qmd

#### Start Date
Start date (**'start_date'**) represents the date when each poll began collecting responses. In the context of our paper, start date is a key variable as it allows us to focus on polling data collected after July 21, 2024—the date Kamala Harris officially announced her presidential campaign. By filtering the dataset to include only polls with a start date after this announcement, we ensure that each poll reflects voter sentiment with Harris as an active candidate, enabling a more accurate comparison between her and Donald Trump. @fig-start-date-distribution displays the distribution of polling start dates from late July to mid-October 2024, showing when polling efforts began across key battleground states. The histogram reveals peaks in polling activity, particularly in mid-August, early September, and late September, indicating periods of heightened interest or campaign events that likely prompted increased polling.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-start-date-distribution
#| fig-cap: "Histogram illustrating the distribution of polling start dates for key battleground states. Displays the frequency of polling activities initiated over time, with a notable peak on September 14, indicating a surge in polling efforts as the election approached."

# Distribution of start_date with x-axis labels every 15 days
ggplot(clean_poll_data, aes(x = start_date)) +
  geom_histogram(bins = 30, fill = "lightblue", color = "black") +
  labs(
       x = "Start Date",
       y = "Count") +
  scale_x_date(date_breaks = "15 days", date_labels = "%b %d") +  # Adjust x-axis labels
  theme_minimal()
```
This distribution provides insights into the timing and intensity of polling efforts throughout the campaign season. By including only polls initiated after Harris’s campaign launch, we capture voter preferences in a context where both major candidates are actively campaigning, thus making the polling data more relevant for direct comparisons. This filtered timeline ensures our model focuses on data that reflects the competitive dynamics between Harris and Trump, enhancing the validity of our predictive analysis as we approach Election Day.

>>>>

#### Start Date
Start date (**'start_date'**) represents the date when each poll began collecting responses. In the context of our paper, start date is a key variable as it allows us to focus on polling data collected after July 21, 2024—the date Kamala Harris officially announced her presidential campaign. By filtering the dataset to include only polls with a start date after this announcement, we ensure that each poll reflects voter sentiment with Harris as an active candidate, enabling a more accurate comparison between her and Donald Trump.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-start-date-distribution
#| fig-cap: "Histogram illustrating the distribution of polling start dates for key battleground states. Displays the frequency of polling activities initiated over time, with a notable peak on September 14, indicating a surge in polling efforts as the election approached."

# Distribution of start_date with x-axis labels every 15 days
ggplot(clean_poll_data, aes(x = start_date)) +
  geom_histogram(bins = 30, fill = "lightblue", color = "black") +
  labs(
       x = "Start Date",
       y = "Count") +
  scale_x_date(date_breaks = "15 days", date_labels = "%b %d") +  # Adjust x-axis labels
  theme_minimal()
```
@fig-start-date-distribution displays the distribution of polling start dates from late July to mid-October 2024, showing when polling efforts began across key battleground states. The histogram reveals peaks in polling activity, particularly in mid-August, early September, and late September, indicating periods of heightened interest or campaign events that likely prompted increased polling. This distribution provides insights into the timing and intensity of polling efforts throughout the campaign season. By including only polls initiated after Harris’s campaign launch, we capture voter preferences in a context where both major candidates are actively campaigning, thus making the polling data more relevant for direct comparisons. This filtered timeline ensures our model focuses on data that reflects the competitive dynamics between Harris and Trump, enhancing the validity of our predictive analysis as we approach Election Day.
